---
title: "Cours R Data Analytics Marketing @TBS"
author: "Adam Green and SylvieB" 
from R for Marketing Research and Analytics by Chris Chapman and Elea McDonnell Feit 
date: "18/10/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Packages
library(tidyverse)
library(summarytools)
```


## INTRO


# Store data
# ==========
```{r}
store.num <- factor(c(3, 14, 21, 32, 54)) # store id
store.rev <- c(543, 654, 345, 678, 234)   # store revenue, $K
store.visits <- c(45, 78, 32, 56, 34)     # visits, 1000s
store.manager <- c("Annie", "Bert", "Carla", "Dave", "Ella")

(store.df <- data.frame(store.num, store.rev, store.visits,
                        store.manager, stringsAsFactors=T))

str(store.df)
```




# Some data checks
# ==========
```{r}
summary(store.df)   # always recommended!

store.df$store.manager
mean(store.df$store.rev)
```




# Read and write CSVs
# ==========
```{r}
write.csv(store.df, row.names=FALSE)
write.csv(store.df, file="store-df.csv", row.names=FALSE)
read.csv("store-df.csv")  # "file=" is optional
```




# Exercise!
# ==========
```{r}
library(car)    # install.packages("car") if needed
data(Salaries)
```




# One Set of Answers
# ==========
```{r}
dim(Salaries)                             # or even better: str(Salaries) or glimpse(Salaries)

str(Salaries)
glimpse(Salaries)


sum(Salaries$yrs.service > 40)


Salaries[Salaries$yrs.service > 20, ]      # output not shown

mean(Salaries[Salaries$yrs.service > 20, "salary"])

?Salaries

```




# Loading and saving raw data formats
# ==========

```{r}

save(store.df, file="store-df-backup.RData")

rm(store.df) #rm used to delete objects from the memory. It can be used with ls() function to delete all objects     

mean(store.df$store.rev)     # error

load("store-df-backup.RData")
mean(store.df$store.rev)     # works now
```



# Loading data has silent overwrite
# ==========

```{r}
store.df <- 5
store.df
load("store-df-backup.RData")
store.df
```





####################################"

## 1. Describing Data
 

# Load the data
# ==========

```{r}

store.df <- read.csv("http://goo.gl/QPDdMl")
summary(store.df)

```



# Descriptives 1
# ==========
```{r}
table(store.df$p1price)

prop.table(table(store.df$p1price))
```




# Table as an object
# ==========
```{r}
p1.table <- table(store.df$p1price)
p1.table
p1.table[3]
str(p1.table)
```




# Plotting a table (basic)
# ==========

```{r}
plot(p1.table)
```




# Two-way tables
# ==========
```{r}
table(store.df$p1price, store.df$p1prom)
```




# Core Descriptive Functions
# ==========

```{r}
min(store.df$p1sales)
max(store.df$p2sales)
mean(store.df$p1prom)
median(store.df$p2sales)


var(store.df$p1sales)
sd(store.df$p1sales)
IQR(store.df$p1sales)
mad(store.df$p1sales)
```




# Percentile (Quantile) function
# ==========

```{r}

quantile(store.df$p1sales)   # default = 0:4*0.25
quantile(store.df$p1sales, probs=c(0.25, 0.75)) # Interquartile
quantile(store.df$p1sales, probs=c(0.025, 0.975)) # central 95%
quantile(store.df$p1sales, probs=1:10/10)  # shortcut
```



# Summary of data frame
# ==========
```{r}
summary(store.df)
```




# Summary of data frame elements
# ==========

```{r}

summary(store.df$p1sales)
summary(store.df$p1sales, digits=2)  # round output
```



# Visualization: Steps to Prettify (1)
# ==========
```{r}

hist(store.df$p1sales)
```



# Improve it with labels
# ==========

```{r}
hist(store.df$p1sales, 
     main="Product 1 Weekly Sales Frequencies, All Stores",
     xlab="Product 1 Sales (Units)",
     ylab="Count" )
```

           


# Make it more granular and colorful
# ==========
```{r}
hist(store.df$p1sales, 
     main="Product 1 Weekly Sales Frequencies, All Stores",
     xlab="Product 1 Sales (Units)",
     ylab="Count",
     breaks=100,             # more columns 
     col="lightblue")       # color the bars
```




# Change counts to proportions
# ==========
```{r}
hist(store.df$p1sales, 
     main="Product 1 Weekly Sales Frequencies, All Stores",
     xlab="Product 1 Sales (Units)",
     ylab="Relative frequency", # changed
     breaks=30, 
     col="lightblue", 
     freq=FALSE )                # freq=FALSE for density
```




# Add density curve
# ==========
```{r}

hist(store.df$p1sales, 
     main="Product 1 Weekly Sales Frequencies, All Stores",
     xlab="Product 1 Sales", ylab="Relative frequency",
     breaks=30, col="lightblue", freq=FALSE)

lines(density(store.df$p1sales, bw=10),  # bw = smoothing
      type="l", col="darkred", lwd=2)    # lwd = line width
```



# Boxplot 
# ==========
```{r}

str(store.df)
boxplot(store.df$p2sales, xlab="Weekly sales", ylab="P2",
        main="Weekly sales of P2, All stores", horizontal=TRUE)
```





# Boxplot broken out by factor
# ==========
```{r}

boxplot(store.df$p2sales ~ store.df$storeNum, horizontal=TRUE,
     ylab="Store", xlab="Weekly unit sales", las=1,
     main="Weekly Sales of P2 by Store")
```




# Boxplot with data and axes
# ==========

```{r}
boxplot(p2sales ~ p2prom, data=store.df, horizontal=TRUE, 
        yaxt="n", ylab="P2 promoted in store", 
        xlab="Weekly sales", main="Sales of P2 vs promotion")
axis(side=2, at=c(1,2), labels=c("No", "Yes"), las=1)
```


# Nicer boxplot with ggplot2

```{r}
library(tidyverse)
library(hrbrthemes)
library(viridis)
library(RColorBrewer)


str(store.df)
store.df$p2prom <- as.factor(store.df$p2prom)

# Rename items of factors "Stim"Promotions"
levels(store.df$p2prom)[levels(store.df$p2prom)=="0"] <- "No promotion"
levels(store.df$p2prom)[levels(store.df$p2prom)=="1"] <- "Promotion"

store.df %>%
  ggplot(aes(x=p2prom, y=p2sales, fill=p2prom)) +
    geom_boxplot() +
    scale_fill_manual(values = c("#edae49", "#00798c"))+
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    theme_ipsum() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)
    ) +
    ggtitle("Sales of P2 vs promotion") +
    xlab("")




```



```{r}

plot(ecdf(store.df$p1sales),
     main="Cumulative distribution of P1 Weekly Sales",
     ylab="Cumulative Proportion",
     xlab=c("P1 weekly sales, all stores", "90% of weeks sold <= 171 units"),
     yaxt="n")
axis(side=2, at=seq(0, 1, by=0.1), las=1, 
     labels=paste(seq(0,100,by=10), "%", sep=""))
# add lines for 90%
abline(h=0.9, lty=3)
abline(v=quantile(store.df$p1sales, pr=0.9), lty=3)
```





# by()
# ==========
```{r}
by(store.df$p1sales, store.df$storeNum, mean)
```




# aggregate()
# ==========
```{r}
storeMean <- aggregate(store.df$p1sales, 
                       by=list(store=store.df$storeNum), mean)
storeMean
```




# Exercise!
# ==========
```{r}
library(car)    # install.packages("car") if needed
data(Salaries)
```




# Answers (1)
# ==========
```{r}

table(Salaries$rank, Salaries$sex)
prop.table(table(Salaries$rank, Salaries$sex))
prop.table(table(Salaries$rank, Salaries$sex), margin=2)
```



# Answers (2)
# ==========

```{r}
hist(Salaries$yrs.service, freq=FALSE)
lines(density(Salaries$yrs.service), col="red")
```




# Answers (3)
# ==========

```{r}

boxplot(Salaries$salary)
```



# Answers (4)
# ==========

```{r}
boxplot(Salaries$salary ~ Salaries$rank, horizontal=TRUE)
```




# Indexing with tables
# ==========

```{r}
table(store.df$p1price, store.df$p1prom)

p1.table2 <- table(store.df$p1price, store.df$p1prom)
p1.table2[, 2] / (p1.table2[, 1] + p1.table2[, 2])
```




# Describe (psych package)
# ==========

```{r}
library(psych)   # must install first
describe(store.df)
```




# Aggregate sales by country
# ==========

```{r}
p1sales.sum <- aggregate(store.df$p1sales, 
                         by=list(country=store.df$country), sum)
p1sales.sum

```



# Plot sales by country with rworldmap()
# ==========

```{r}

library(rworldmap)    # must be installed
library(RColorBrewer) # must be installed

p1sales.map <- joinCountryData2Map(p1sales.sum, 
                                   joinCode = "ISO2", 
                                   nameJoinColumn = "country")
```



# Draw the map
# ==========

```{r}
mapCountryData(p1sales.map, nameColumnToPlot="x", 
               mapTitle="Total P1 sales by Country",
               colourPalette=brewer.pal(7, "Greens"), 
               catMethod="fixedWidth", addLegend=FALSE)
```


           


####################################"

## 2. Comparing Groups: Statistical Tests



# Load the data 
# ==========

```{r}
seg.df <- read.csv("http://goo.gl/qw303p")
summary(seg.df)
str(seg.df)
```




# Chi-square test
# ==========
```{r}
tmp.tab <- table(rep(c(1:4), times=c(25,25,25,20)))
tmp.tab
chisq.test(tmp.tab)
```




# chisq.test "significant" and "not significant"
# ==========
```{r}
tmp.tab <- table(rep(c(1:4), times=c(25,25,25,20)))
chisq.test(tmp.tab)

tmp.tab <- table(rep(c(1:4), times=c(25,25,25,10)))
tmp.tab
chisq.test(tmp.tab)
```




# chisq.test with segment data
# ==========
```{r}

table(seg.df$Segment)
chisq.test(table(seg.df$Segment))
```



# chisq.test with segment data
# ==========
```{r}
table(seg.df$subscribe, seg.df$ownHome)
chisq.test(table(seg.df$subscribe, seg.df$ownHome))

chisq.test(table(seg.df$subscribe, seg.df$ownHome), correct=FALSE)
```




# Proportions: binomial test
# ==========
```{r}
binom.test(12, 20, p=0.5)
```




# Proportions: binomial test continued
# ==========
# binom.test(12, 20, p=0.5)

```{r}

binom.test(120, 200, p=0.5)
```



# t-tests
# ==========

```{r}
library(lattice)
bwplot(income ~ ownHome, data=seg.df)
```




# t.test()
# ==========
```{r}
t.test(income ~ ownHome, data=seg.df)
```




# t.test() for a subset() of data
# ==========
```{r}
t.test(income ~ ownHome, data=subset(seg.df, Segment=="Travelers"))
```




# ANOVA basics
# ==========

```{r}
seg.aov.own <- aov(income ~ ownHome, data=seg.df)
anova(seg.aov.own)
```




# ANOVA: Multiple groups
# ==========

```{r}
aggregate(income ~ Segment, mean, data=seg.df)
seg.aov.seg <- aov(income ~ Segment, data=seg.df)
anova(seg.aov.seg)
```





# ANOVA with Segment + Ownership
# ==========

```{r}
anova(aov(income ~ Segment + ownHome, data=seg.df))

anova(aov(income ~ ownHome, data=seg.df))
```




# ANOVA with interaction
# ==========

```{r}
anova(aov(income ~ Segment * ownHome, data=seg.df))

anova(aov(income ~ Segment + ownHome + Segment:ownHome, data=seg.df))
```




# Model Comparison
# ==========

```{r}

anova(aov(income ~ Segment,           data=seg.df),
      aov(income ~ Segment + ownHome, data=seg.df))
```




# Visualization: ANOVA Group means
# ==========
# install.packages("multcomp")     # if needed

```{r}
library(multcomp)
seg.aov <- aov(income ~ -1 + Segment, data=seg.df)   # model w/o int.
by.seg  <- glht(seg.aov)                             # means and CIs
plot(by.seg, xlab="Income", main="Mean Income by Segment (95% CI)")
```




# Exercises (Basic)
# ==========

```{r}

library(car)    # install.packages("car") if needed
data(Salaries)
```



# Answers (1)
# ==========

```{r}
with(Salaries, prop.table(table(discipline, sex), margin=1))
with(Salaries, chisq.test(table(discipline, sex)))
```




# Answers (2)
# ==========

```{r}
aggregate(salary ~ sex, data=Salaries, mean)
anova(aov(salary ~ sex, data=Salaries))
```




# Answers (3)
# ==========
# install.packages("multcomp")     # if needed

```{r}
library(multcomp)
salary.aov <- aov(salary ~ -1 + sex, data=Salaries)
by.sex  <- glht(salary.aov)                           
plot(by.sex, xlab="Salary", main="Mean Salary with 95% CI")
```




####################################"

## 3. Identifying Drivers of Outcomes: Linear Models


# Satisfaction survey data
# ==========
```{r}

sat.df <- read.csv("http://goo.gl/HKnl74")
```



# Inspecting the data
# ==========
```{r}
summary(sat.df)
str(sat.df)
```




# Plotting the data
# ==========
```{r}
library(gpairs)
gpairs(sat.df)
```




# Transforming some variables
# ==========
```{r}
hist(sat.df$distance)

sat.df$logdist <- log(sat.df$distance)
hist(sat.df$logdist)
```




# corrplot: an alternative to the scatterplot matrix
# ==========

```{r}

library(corrplot)
corrplot.mixed(cor(sat.df[ , c(2, 4:9)]), upper="ellipse") 
```



# Fitting a model with one predictor
# ==========

```{r}
lm(overall ~ rides, data=sat.df)

-94.962 + 1.703*95
```




# Model objects
# ==========

```{r}
m1 <- lm(overall ~ rides, data=sat.df)
m1
str(m1)
```


# A plot of the model
# ==========

```{r}

plot(overall ~ rides, data=sat.df,
     xlab="Satisfaction with Rides", ylab="Overall Satisfaction")
abline(m1, col='blue')
```



# Model summary
# ==========

```{r}
summary(m1)
```


# Model assumptions
# ==========

```{r}
x <- rnorm(500)
y <- x^2 + rnorm(500)
toy.model <- lm(y ~ x)
summary(toy.model)


```




# Model assumptions
# ==========
```{r}
plot(y ~ x)
abline(toy.model)

#other try:
x <- rnorm(500)
y <- 100+ rnorm(500)
toy.model <- lm(y ~ x)
summary(toy.model)
```




# Standard plots for assessing model fit
# ==========
```{r}
par(mfrow=c(2,2))
plot(m1)

#Reminder:
#m1 <- lm(overall ~ rides, data=sat.df)
```




# Inspecting outliers
# ==========

```{r}
#see last plot Residual vs. Leverage in plot(m1)
sat.df[c(57, 129, 295),]
```



# Fitting a model with multiple predictors
# ==========

```{r}
m2 <- lm(overall ~ rides + games + wait + clean, data=sat.df)
summary(m2)
```


# Presenting the findings
# ==========

```{r}
library(coefplot)
coefplot(m2, intercept=FALSE, outerCI=1.96, lwdOuter=1.5,
ylab="Rating of Feature", 
xlab="Association with Overall Satisfaction")
```




# Comparing two models: R-squared
# ==========

```{r}
summary(m1)$r.squared # single predictor: rides
summary(m2)$r.squared # multple predictors
summary(m1)$adj.r.squared
summary(m2)$adj.r.squared
```




# Comparing models: visually
# ==========
```{r}
plot(sat.df$overall, fitted(m1), col='red',
     xlim=c(0,100), ylim=c(0,100),
     xlab="Actual Overall Satisfaction", ylab="Fitted Overall Satisfaction")
points(sat.df$overall, fitted(m2), col='blue')
legend("topleft", legend=c("model 1", "model 2"), 
       col=c("red", "blue"), pch=1)
```




# Comparing models: formal statistical test
# ==========

```{r}
anova(m1, m2)
```


# Making predictions
# ==========

```{r}
coef(m2)["(Intercept)"] + coef(m2)["rides"]*100 + coef(m2)["games"]*100 + 
  coef(m2)["wait"]*100 + coef(m2)["clean"]*100 

coef(m2)%*%c(1, 100, 100, 100, 100)


```


# Making predictions
# ==========

```{r}

predict(m2, sat.df[1:10, ])  # first 10 observations
fitted(m2)[1:10]            # same, automatically in model object
```




#################################################################################################################################################################################""


