---
title: "The Most Human Bot Study D"
author: "Adam and Sylvie"
date: "14/10/2023"
output:
  html_document:
    toc: true
  pdf_document: 
    toc: true
---

#Install the packages first


#Libraries

```{r Libraries, message=F, warning=F, include=FALSE}


library(tidyverse)
library(extrafont)
library(hrbrthemes)
library(ggthemes)
library(gridExtra)
library(lme4)
library(lmerTest)
library(stargazer)
library(summarytools)
library(PerformanceAnalytics)
library(ggplot2)
library(effects)


```

 


# Load the data (This is an Rdata file - No need to specify the location of the file if the file is in the same folder)


```{r}

load("StudyD.rdata")



```



# Age and gender/ and list of variables in the dataframe

```{r}


mean(StudyD$Age)
sd(StudyD$Age)


summary(StudyD$Gender)


str(StudyD)

```


# Recap: List of main variables in the Dataframe

IV: INDEPENDANT VARIABLES
Manip (male or female chatbot)

DV:DEPENDANT VARIABLES
Attitude
Uniqueness
Credibility
Trust
ScaleAnimalHuman
ScaleRobotHuman 
Competent
Warm
Moral
Mechanical  
HumanRecommendation

Controls:
Gender
Age
Children
Stereotypes
TechReadiness
Narcissism 


# Rename items of factors 

```{r}

levels(StudyD$Manip)[levels(StudyD$Manip)=="1"] <- "Male"
levels(StudyD$Manip)[levels(StudyD$Manip)=="2"] <- "Female"


levels(StudyD$Gender)[levels(StudyD$Gender)=="1"] <- "Men"
levels(StudyD$Gender)[levels(StudyD$Gender)=="2"] <- "Women"


levels(StudyD$Children)[levels(StudyD$Children)=="1"] <- "Yes"
levels(StudyD$Children)[levels(StudyD$Children)=="2"] <- "No"

```


# Find & change the order of the items

```{r}

levels(StudyD$Manip)
levels(StudyD$Gender)
levels(StudyD$Children)
summary(StudyD$Children)

# Change the order of the items
StudyD$Children <- factor(StudyD$Children, levels = c("No", "Yes"))
levels(StudyD$Children)
summary(StudyD$Children)


```


# Descriptives: comparing the scores between the male and the female chatbots on several variables

```{r}


StudyD %>%
  group_by(Manip) %>%
  summarize(mean(ScaleRobotHuman), 
            sd(ScaleRobotHuman))

StudyD %>%
  group_by(Manip) %>%
  summarize(mean(ScaleAnimalHuman), 
            sd(ScaleAnimalHuman))


StudyD %>%
  group_by(Manip) %>%
  summarize(mean(Trust), 
            sd(Trust))


StudyD %>%
  group_by(Manip) %>%
  summarize(mean(Credibility), 
            sd(Credibility))


StudyD %>%
  group_by(Manip) %>%
  summarize(mean(Attitude), 
            sd(Attitude))

```



## Linear Models by Robot Gender (IV)  with covariates 

```{r}


lm1 = lm (Attitude ~ Manip + Stereotypes + Age + Gender + Children + Narcissism  + TechReadiness, data = StudyD)
summary(lm1)

lm2 = lm (Uniqueness ~ Manip + Age + Gender + Children + Narcissism + Stereotypes + TechReadiness, data = StudyD)
summary(lm2)

lm3 = lm (Credibility ~ Manip + Age + Gender + Children + Narcissism + Stereotypes + TechReadiness, data = StudyD)
summary(lm3)

lm4 = lm (Trust ~ Manip + Age + Gender + Children + Narcissism + Stereotypes + TechReadiness, data = StudyD)
summary(lm4)

lm5 = lm (ScaleAnimalHuman ~ Manip + Age + Gender + Children + Narcissism + Stereotypes + TechReadiness, data = StudyD)
summary(lm5)

lm6 = lm (ScaleRobotHuman ~ Manip + Age + Gender + Children + Narcissism + Stereotypes + TechReadiness, data = StudyD)
summary(lm6)

lm7 = lm (CompWarmMoral ~ Manip + Age + Gender + Children + Narcissism + Stereotypes + TechReadiness, data = StudyD)
summary(lm7)

lm8 = lm (Competent ~ Manip + Age + Gender + Children + Narcissism + Stereotypes + TechReadiness, data = StudyD)
summary(lm8)

lm9 = lm (Warm ~ Manip + Age + Gender + Children + Narcissism + Stereotypes + TechReadiness, data = StudyD)
summary(lm9)

lm10 = lm (Moral ~ Manip + Age + Gender + Children + Narcissism + Stereotypes + TechReadiness, data = StudyD)
summary(lm10)

lm11 = lm (Mechanical ~ Manip + Age + Gender + Children + Narcissism + Stereotypes + TechReadiness, data = StudyD)
summary(lm11)

lm12 = lm (Stereotypes  ~ Manip + Age + Gender + Children + Narcissism + TechReadiness, data = StudyD)
summary(lm12)





```




## Recap table using the stargazer package 


```{r}

stargazer(lm11, lm5, lm6, lm8, lm9, lm10, lm4, lm3, lm2, lm1, 
          type = "text", 
          digits = 2,  
          star.cutoffs = c(0.05, 0.01, 0.001), 
          out="StudyD.htm",
          dep.var.labels = c("Mechanical", "ScaleAnimalHuman", "ScaleRobotHuman", "Competent", "Warm", "Moral","Trust","Credibility", "Uniqueness", "Attitude"), 
          covariate.labels = c("AI: Female", "Age", "Resp Gender: Women", "Children", "Narcissism", "Stereotypes", "TechReadiness"),
          omit.stat = c("rsq", "f", "adj.rsq", "ser"))


```



## Plots 

Geom_Density 


```{r}

StudyD$Manip <- as.factor(StudyD$Manip)

ggplot(StudyD, aes(ScaleRobotHuman, fill = Manip)) +
  geom_density(alpha=0.5) +
  xlab("From robot to Human") +
  scale_fill_manual(values=c("darkgrey","darkcyan"))+
  theme_bw()

ggplot(StudyD, aes(Warm, fill = Manip)) +
  geom_density(alpha=0.5) +
  xlab("Warm") +
  scale_fill_manual(values=c("darkgrey","darkcyan"))+
  theme_bw()



----------
  
# you can also save the plot as a png file:
  
plot2 <-ggplot(StudyD, aes(Warm, fill = Manip)) +
  geom_density(alpha=0.5) +
  xlab("Warm") +
  scale_fill_manual(values=c("darkgrey","darkcyan"))+
  theme_bw()

ggsave("plot2.png")





```



BOXPLOT 

```{r}

# Warm

Plota <- ggplot(StudyD, aes(Warm, fill = Manip))+
  geom_boxplot ()+
  scale_color_manual(values=c("darkgrey", "cadetblue3"))+
  scale_fill_manual(values = c("darkgrey", "cadetblue3"))+
  labs(title="Warm perceptions",x="Warm", y = "Manip")+
  theme(legend.position="none")
Plota  


```


## mediation
You need to run the Process function fist (see script file Process).
& You need to transform the factors as numeric variables to use the Process function.


```{r}

#super useful line of code. shows if people have a better attitude towards manip if they view as warm.
#can change manip to woman. So you see if people have a better attitude to woman if they percieve them to be warm

StudyD$Manip <- as.numeric(StudyD$Manip)
StudyD$Gender <- as.numeric(StudyD$Gender)
StudyD$Children <- as.numeric(StudyD$Children)


process(data = StudyD, y = "Attitude", x = "Manip", m ="Warm", cov = c("Age", "Gender", "Children","TechReadiness"), model = 4)

#if confidence interval include 0 it's not significant. If interval values are both above or below zero its significant (positively or negatively)

```

